\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-01-22 manuscript/manuscript.tex
responded to some comments

\jy{Clean up the tables. Use percentage for power. Keep three effective
  digits. Why are there so many decimal places? }

\jy{Only three sample sizes will be enough. Sample size 800 or higher give
  power~1. Only report nominal size 0.05 would be ok. May consider presenting
  the intervals in a figure.}

\input{tables/rr_100}

@@

\input{tables/rr_1600}

\input{tables/rr_3200}

From Table~\ref{table:rr_100}, we can see that when $n = 100$, the rejection 
rate may 
be quite low, especially for lower values of $\alpha$. From 
Table~\ref{table:rr_200}, 
the rejection rates are a little higher for $n = 200$, but they may still be 
drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
from Table~\ref{table:rr_400} that the rejection rate
is consistently above 50\%. For larger sample sizes, the rejection rate is 
consistently above 90\%. We can also
observe that the rejection rate is slightly higher for the $\gamma(8, 1)$ sample 
than for 
the $N(8, 8)$. As the strength of the temporal dependence increases, the 
rejection rate decreases, and the rejection
rate appears to be slightly higher for negative temporal dependence versus 
positive temporal dependence values of the same strength.

As shown in Tables~\ref{table:rr_800}, \ref{table:rr_1600}, and 
\ref{table:rr_3200}, the rejection rates for these settings are very 
high (almost 1), indicating that under $H_A$, the test is very powerful 
(low probability of failed rejection $\beta$) when a large enough
sample size is used.

@@

\jy{Normal was not rejected for 1 year. How about 2 year, 3 year, 4 year?}

>>>>

\jy{Clean up the tables. Use percentage for power. Keep three effective
  digits. Why are there so many decimal places? }
\mc{reduced number of digits}

\jy{Only three sample sizes will be enough. Sample size 800 or higher give
  power~1. Only report nominal size 0.05 would be ok. May consider presenting
  the intervals in a figure.}
\mc{only included three sample sizes and for alpha $=$ 0.05}

@@

From 
Table~\ref{table:rr_200}, 
the rejection rates are a little higher for $n = 200$, but they may still be 
drop below 50\% is the $\alpha = 0.1$. Once $n$ reaches 400, we can observe 
from Table~\ref{table:rr_400} that the rejection rate
is consistently above 50\%. For larger sample sizes, the rejection rate is 
consistently above 90\%. We can also
observe that the rejection rate is slightly higher for the $\gamma(8, 1)$ sample 
than for 
the $N(8, 8)$. As the strength of the temporal dependence increases, the 
rejection rate decreases, and the rejection
rate appears to be slightly higher for negative temporal dependence versus 
positive temporal dependence values of the same strength.

As shown in Tables~\ref{table:rr_800}, the rejection rates for this settings 
are very 
high (almost 1), indicating that under $H_A$, the test is very powerful 
(low probability of failed rejection $\beta$) when a large enough
sample size is used.

@@

\jy{Normal was not rejected for 1 year. How about 2 year, 3 year, 4 year?}
\mc{tried these sample sizes, normal is rejected for all three might want to
try 1.5 years}
